---
title: "USArrests Data Set Analysis"
author: "Mominul Islam"
date: "1/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Scenario 

This analysis is going to determine whether a state in the USA is dangerous
regarding rape, murder and assault,as well as give an warning message if the
state name of the user's input is invalid. The USArrests data set is already
in **RStudio** built-in system, therefore, there is no need to import data 
from external sources.


### Investigating the data structure and few rows from the dataset.

```{r cars}
str(USArrests)
head(USArrests)

```
### Creating a function to determine wheather a state is dangerous regarding
### rape, murder and assault,as well as setting the warning message if the state
### name of the user's input is invalid.

```{r}
dangerious_state<- function(state_name){
  if (!state_name %in% row.names(USArrests)){ 
    print("Invalid State Name") #Return invalid state name If the state name not in data set.
  }else if (USArrests[state_name, "Murder"] > mean(USArrests[, "Murder"]) &
           USArrests[state_name, "Rape"] > mean(USArrests[, "Rape"]) &
            USArrests[state_name, "Assault"] > mean(USArrests[, "Assault"])){
              print("Dangerious State")
            }else{
              print("Safe State")
            }
}
dangerious_state("California") ## Calling the function.
dangerious_state("Arizona")
dangerious_state("Arkansas")
dangerious_state("Helsinki")
dangerious_state("Berlin")


```





